Approximation as Differentiation: Notes

### 2025-05-16 main/formal-structures.tex
Prefer direct composition notation for reindexing functor.

Now consider the total category $\Fam(\LatGal)$, which is our basic setting for interpreting first-order
programs for Galois slicing. This has as objects $(X, \partial X)$, all pairs of a set $X$ and and for every
$x \in X$, a bounded lattice $\partial X(x)$, and as morphisms $(X, \partial X) \to (Y, \partial Y)$, all
pairs $(f, \partial f)$ of a function $f: X \to Y$ and for every $x \in X$, a Galois connection $\partial
f(x): \partial X(x) \to \partial Y(f(x))$, as required. The pullback (reindexing) along $f$ in the composition
$(g, \partial g) \comp (f, \partial f) = (g \comp f, \reindex{\partial g}{f} \comp \partial f)$ selects the
appropriate lattice of approximations and Galois connection at each point, using the baseline (unapproximated)
function $f$.

>>>>

Now consider the total category $\Fam(\LatGal)$, which is our basic setting for interpreting first-order
programs for Galois slicing. This has as objects $(X, \partial X)$, all pairs of a set $X$ and and for every
$x \in X$, a bounded lattice $\partial X(x)$, and as morphisms $(X, \partial X) \to (Y, \partial Y)$, all
pairs $(f, \partial f)$ of a function $f: X \to Y$ and for every $x \in X$, a Galois connection $\partial
f(x): \partial X(x) \to \partial Y(f(x))$, as required. The pullback (reindexing) along $f$ in the composition
$(g, \partial g) \comp (f, \partial f) = (g \comp f, \partial g \comp f \comp \partial f)$ selects the
appropriate lattice of approximations and Galois connection at each point, using the baseline (unapproximated)
function $f$.
